%% OBLIGE: Fast, Precise Root-Cause Diagnosis of eBPF Verification Failures
%% Target: OSDI / SOSP / EuroSys (12 pages, anonymous review)
\documentclass[sigplan,10pt,anonymous,review]{acmart}

\usepackage{listings}
\usepackage{xcolor}
\usepackage{microtype}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{url}
\usepackage{subcaption}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,fit}

\newcommand{\sys}{\textsc{Oblige}\xspace}
\usepackage{xspace}

%% Suppress acmart copyright block for draft
\setcopyright{none}
\acmDOI{}
\acmISBN{}
\acmConference[EuroSys '27]{ACM European Conference on Computer Systems}{April 2027}{Rotterdam, Netherlands}
\acmYear{2027}

%% Listings style for verifier output / C code
\lstdefinestyle{verifier}{
  basicstyle=\ttfamily\scriptsize,
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  frame=none,
  aboveskip=2pt,
  belowskip=2pt,
}

\lstdefinestyle{oblige}{
  basicstyle=\ttfamily\scriptsize,
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  frame=none,
  aboveskip=2pt,
  belowskip=2pt,
  moredelim=[is][\bfseries\color{red!70!black}]{/*bold*/}{/*end*/},
}

\lstdefinestyle{ccode}{
  language=C,
  basicstyle=\ttfamily\scriptsize,
  keywordstyle=\bfseries,
  commentstyle=\itshape\color{gray},
  breaklines=true,
  columns=fullflexible,
  keepspaces=true,
  frame=none,
  aboveskip=2pt,
  belowskip=2pt,
  numbers=left,
  numberstyle=\tiny\color{gray},
  numbersep=5pt,
}

%% Theorem environments (acmart provides amsthm)
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}

%% Tighter spacing for figures
\setlength{\floatsep}{4pt}
\setlength{\textfloatsep}{6pt}
\setlength{\intextsep}{4pt}

%% Suppress widow/orphan lines
\widowpenalty=10000
\clubpenalty=10000

%% Allow slight flexibility to prevent overfull hboxes from inline \texttt{} tokens
\emergencystretch=1.5em

%% Fix fancyhdr headheight warning
\setlength{\headheight}{18.5pt}
\addtolength{\topmargin}{-5.5pt}

\begin{document}

\title{\sys: Fast, Precise Root-Cause Diagnosis of eBPF Verification Failures}

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011008.10011024.10011025</concept_id>
       <concept_desc>Software and its engineering~Compilers</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
       <concept_id>10011007.10011006.10011073.10011074</concept_id>
       <concept_desc>Software and its engineering~Software verification and validation</concept_desc>
       <concept_significance>500</concept_significance>
   </concept>
   <concept>
       <concept_id>10010520.10010521.10010537.10010538</concept_id>
       <concept_desc>Computer systems organization~Operating systems</concept_desc>
       <concept_significance>300</concept_significance>
   </concept>
</ccs2012>
\end{CCSXML}
\ccsdesc[500]{Software and its engineering~Compilers}
\ccsdesc[500]{Software and its engineering~Software verification and validation}
\ccsdesc[300]{Computer systems organization~Operating systems}

\keywords{eBPF, program verification, static analysis, abstract interpretation,
compiler diagnostics, proof trace analysis}

\begin{abstract}
eBPF programs must pass a complex static verifier whose rejection messages
are notoriously opaque---developers receive verbose, thousand-line logs
pinpointing symptoms but obscuring the underlying cause.
Fixing these rejections requires understanding \emph{where} the safety
proof broke, not just \emph{that} it broke; our analysis of 591
verifier-related commits shows that 63.6\% are proof-reshaping workarounds
where the source code is correct but the verifier's abstract domain loses
track of the developer's safety argument through LLVM's lowering.

We observe that the verifier's execution trace is a complete record of a
proof attempt---a sequence of per-instruction abstract states.  By analyzing
\emph{abstract state transitions} across this trace (bounds collapses, type
downgrades, provenance loss), \sys automatically locates where the safety
proof broke and why, without requiring knowledge of which specific safety
condition was checked.  The transition pattern itself classifies the failure:
a safety property never established indicates a source bug; one established
then lost indicates a compiler-induced lowering artifact.

Evaluating \sys on 302 real-world verifier rejections from kernel selftests
and production systems, we achieve 94\% obligation coverage, pinpoint the
exact root cause in 67\% of previously undiagnosable compilation-induced
failures, and boost automated code-repair accuracy by 30 percentage points.
\sys operates entirely in userspace, incurs just 25.3\,ms median latency per
diagnosis, and requires no kernel modifications.
\end{abstract}

\maketitle

%% ==============================
\section{Introduction}
\label{sec:intro}
%% ==============================

% --- Para 1: System scene + problem ---
eBPF is the foundation for critical kernel extensions powering security
enforcement (Cilium, Katran), performance tracing (bcc, bpftrace), and
networking infrastructure in production Linux deployments. Ensuring safety,
however, requires each eBPF program to pass a mandatory static verifier, an
abstract interpreter that rigorously checks all instructions before execution.
Unfortunately, when verification fails, developers confront overwhelmingly
verbose diagnostic logs often spanning thousands of lines. These logs reveal
only symptoms at rejection points, leaving the root cause---typically a safety
proof destroyed deep within compiler-generated instructions---buried hundreds
of lines earlier. Consequently, debugging verifier rejections has become the
single largest productivity bottleneck in eBPF development, as confirmed by a
recent Linux Foundation security audit~\cite{nccaudit2024} and extensive
developer frustration on Stack Overflow~\cite{deokar2024}.

% --- Para 2: Evidence + why existing fails ---
Analyzing 591 verifier-related commits from four production eBPF projects
(Cilium, Katran, bpftrace, Aya), we find that 63.6\% are
proof-reshaping workarounds: the source code is correct, but the verifier's
abstract domain cannot track the developer's safety argument through LLVM's
lowering.  These rejections are inherent to the verifier's design and cannot
be eliminated by better diagnostics alone---but fixing them correctly
requires knowing \emph{where} the safety proof broke, which current tools
cannot provide. We find that
existing solutions fundamentally misunderstand the structure embedded within
verification traces: current tools either rely on shallow regular expressions
applied only to the final rejection message~\cite{prettyverifier2025} or feed
entire raw logs to general-purpose language
models~\cite{kgent2024}, neither approach recognizing the verifier trace as a
structured safety proof attempt.
\label{sec:intro-gap}

% --- Para 3: Key insight ---
Our key insight is that the verifier's execution trace is a complete record of
a proof attempt---a sequence of per-instruction abstract states---and that
analyzing \emph{abstract state transitions} across this trace reveals where
and why the safety proof broke.  The error message identifies which safety
condition was checked (we call this the ``proof obligation,'' used as a focus
mechanism), but the core analysis is detecting the instruction whose abstract
state transition---bounds collapse, type downgrade, provenance loss---caused
the violation.  We call this the ``proof-loss point.''  Crucially, the
transition pattern itself classifies the failure: a safety property never
established in the trace indicates a source-level programming bug, while one
established then lost indicates a compiler-induced lowering artifact.

% --- Figure 1: motivating example ---
\begin{figure*}[t]
\begin{minipage}[t]{0.31\linewidth}
\textbf{Panel A: Source code}
\vspace{2pt}
\begin{lstlisting}[style=ccode, firstnumber=1]
int parse_ext(struct xdp_md *ctx) {
    void *data = (void*)(long)ctx->data;
    void *data_end = (void*)(long)ctx->data_end;
    if (data+sizeof(struct ext) > data_end)
        return XDP_DROP;         // bounds check
    struct ext *e = data;
    // reads guarded by line 3
    __u16 len = __bpf_htons(e->len); // byte-swap
    data += len;                 // REJECTED
    /* "unbounded min value" */
}
\end{lstlisting}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\linewidth}
\textbf{Panel B: Raw verifier output (excerpt)}
\vspace{2pt}
\begin{lstlisting}[style=verifier]
22: R0_w=inv(id=0,umax=65280,
    var_off=(0x0; 0xff00))
    R6_w=inv(id=0,umax=255,
    var_off=(0x0; 0xff))
22: (4f) r0 |= r6
23: R0_w=inv(id=0)   <-- bounds GONE
...
math between pkt pointer and register
with unbounded min value is not allowed
\end{lstlisting}
\vspace{2pt}
\textit{Pretty Verifier output:}
\begin{lstlisting}[style=verifier]
"The value added to the packet pointer
 has an unbounded minimum. Consider
 adding `& 0xFFFF` to bound the value."
\end{lstlisting}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.33\linewidth}
\textbf{Panel C: \sys output}
\vspace{2pt}
\begin{lstlisting}[style=verifier]
error[E005]: lowering_artifact
  -- parse_ext.c
  |
3 | if (data+sizeof(ext) > data_end)
  | ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
  | proof established
  | R5: pkt(off=0) -> pkt(off=4,r=4)
  |
7 | __u16 len = __bpf_htons(e->len);
  | ^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^
  | proof lost: OR destroys bounds
  | R0: scalar(umax=65280) -> scalar
  |
8 | data += len;
  | ^^^^^^^^^^^
  | rejected: pkt_ptr + unbounded
  |
  = note: LLVM lowers htons() to byte-load,
    shift, OR. Verifier cannot track OR result.
  = help: Add clamp: len &= 0xFFFF;
\end{lstlisting}
\end{minipage}
\caption{The motivating example: SO \#70750259.  \textbf{Panel A}: source
code with a correct bounds check at line 3.  \textbf{Panel B}: the verifier's
raw output (60+ lines, excerpt shown) and Pretty Verifier's single-line
response---both pointing at the symptom, not the cause.  \textbf{Panel C}:
{\sys}'s Rust-style multi-span output tracing abstract state transitions through three
source locations: proof established (line 3), proof lost (line 7, OR
instruction destroys bounds), rejected (line 8).}
\Description{Three-panel motivating example. Panel A: C source with bounds check.
Panel B: raw verifier output and Pretty Verifier single-line response.
Panel C: \sys Rust-style multi-span diagnostic with proof-established, proof-lost, and rejected labels.}
\label{fig:motivating}
\end{figure*}

% --- Para 4: System + results ---
Motivated by this insight, we design and implement \sys, a novel userspace
diagnostic engine that detects safety-relevant abstract state transitions
across verifier traces, traces their causal chains back to the root-cause
instruction, and provides concise, Rust-inspired diagnostics pinpointing
exactly where and why the safety proof broke. On 302
diverse real-world verifier failures, \sys achieves 94\% obligation coverage,
correctly identifies previously undiagnosable proof-loss points in 67\% of
lowering-artifact cases, and improves the accuracy of automated
language-model-based code repairs by 30 percentage points. Moreover, \sys
diagnoses verifier failures at a median latency of just 25.3\,ms per case,
entirely in userspace, and without modifying the Linux kernel.

% --- Contributions ---
In summary, this paper makes three main contributions:
\begin{itemize}
  \item Identifies a structured, generalizable framework (abstract state
        transition analysis) that precisely pinpoints verifier root-cause
        failures and systematically classifies failure types
        (\S\ref{sec:obligation-inference}--\S\ref{sec:formal-foundation}).

  \item Designs and implements \sys, a fast userspace diagnostic tool
        leveraging this framework to deliver concise, actionable verifier
        diagnostics
        (\S\ref{sec:state-trace-parsing}--\ref{sec:formal-foundation}).

  \item Demonstrates {\sys}'s practical impact by significantly improving
        diagnosis precision, reducing unnecessary code reshaping, and
        increasing automated fix accuracy on hundreds of real-world verifier
        failures (\S\ref{sec:batch}--\S\ref{sec:latency}).
\end{itemize}

%% ==============================
\section{Background}
%% ==============================

\subsection{The eBPF Verification Pipeline}

eBPF programs are written in C or Rust, compiled by LLVM to BPF bytecode, and
submitted to the kernel via the \texttt{bpf()} syscall.  The Linux verifier
runs before any program executes.  It performs a dataflow-style abstract
interpretation~\cite{cousot1977,gershuni2019simple}: it walks all execution
paths through the bytecode, maintaining per-register abstract state and
enforcing a set of safety properties at each instruction.  Programs that
violate any property are rejected.

The key architectural point is that there are three distinct reasoning levels:
\begin{itemize}
  \item \textbf{Source level.}  The programmer reasons about C/Rust values,
        bounds checks, null checks, and pointer lifetimes.
  \item \textbf{Compiler level.}  LLVM transforms source into BPF bytecode,
        potentially splitting, merging, or reordering computations.
  \item \textbf{Verifier level.}  The verifier reasons about BPF register
        abstract state: types, scalar bounds (\texttt{umin/umax},
        \texttt{smin/smax}), pointer offsets, packet ranges, and provenance IDs.
\end{itemize}
A proof that is valid at the source level can be lost at the verifier level if
LLVM's lowering produces register state that the verifier's abstract domain
cannot represent.  This is the root cause of lowering artifacts.

\subsection{Anatomy of a \texttt{LOG\_LEVEL2} Trace}
\label{sec:trace-anatomy}

When \texttt{log\_level=2} is set in \texttt{BPF\_PROG\_LOAD}, the verifier
emits a complete per-instruction trace interleaving per-register abstract state
(type, scalar bounds, pointer offset, packet range, provenance ID), BTF source
annotations~\cite{linuxbtf}, \texttt{mark\_precise} backtracking chains, and
control flow merge points.  A typical 50-instruction program produces
100--300 lines.  We detail the parsing of each element in~\S\ref{sec:state-trace-parsing}.


%% ==============================
\section{Design: The \sys Diagnostic Engine}
%% ==============================

\subsection{Architecture Overview}

\sys is a five-stage pipeline that transforms a raw \texttt{LOG\_LEVEL2}
verifier trace into a structured multi-span diagnostic.
Figure~\ref{fig:pipeline} shows the architecture.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  stagebox/.style={rectangle, draw, rounded corners, minimum width=2.6cm, minimum height=0.5cm, align=center, font=\small},
  arr/.style={-Latex, thick},
  outbox/.style={rectangle, draw=gray, dashed, rounded corners, minimum width=2.6cm, text width=2.6cm, minimum height=0.4cm, align=center, font=\scriptsize\itshape},
  node distance=0.32cm and 1.0cm
]
  \node[stagebox] (log)    {1. Log Parser};
  \node[stagebox, below=of log] (trace)  {2. State Trace Parser};
  \node[stagebox, below=of trace] (proof) {3. Proof Engine};
  \node[stagebox, below=of proof] (btf)   {4. Source Correlator};
  \node[stagebox, below=of btf]   (rend)  {5. Diagnostic Renderer};

  \node[outbox, right=of log]   (e1) {error\_id, taxonomy class\\(23 patterns)};
  \node[outbox, right=of trace] (e2) {per-insn reg state\\BTF maps, backtracks};
  \node[outbox, right=of proof] (e3) {state transitions\\transition witnesses\\proof lifecycle labels};
  \node[outbox, right=of btf]   (e4) {BTF source spans\\with proof roles};
  \node[outbox, right=of rend]  (e5) {Rust-style text + JSON};

  \draw[arr] (log) -- (trace);
  \draw[arr] (trace) -- (proof);
  \draw[arr] (proof) -- (btf);
  \draw[arr] (btf) -- (rend);
  \draw[arr] (log) -- (e1);
  \draw[arr] (trace) -- (e2);
  \draw[arr] (proof) -- (e3);
  \draw[arr] (btf) -- (e4);
  \draw[arr] (rend) -- (e5);

  \node[above=0.3cm of log, font=\small\bfseries] {Verifier LOG\_LEVEL2 trace};
\end{tikzpicture}
\caption{\sys five-stage pipeline.  Each stage is independently testable;
the proof engine (abstract state transition analysis) is the key novelty.
The full implementation is $\sim$14,613 lines of Python with 268 unit tests.}
\Description{Five-stage pipeline diagram: Log Parser, State Trace Parser, Proof Engine, Source Correlator, Diagnostic Renderer, each with labeled output boxes showing intermediate results.}
\label{fig:pipeline}
\end{figure}

Each stage is independently testable and produces a well-defined intermediate
representation.  The system processes 262 real cases with zero crashes and
a median end-to-end latency of 25.3\,ms.

\subsection{State Trace Parsing}
\label{sec:state-trace-parsing}

The log parser (Stage 1) handles error message identification: it matches
the final error line against 23 error patterns (\sys{}-E001 through E023),
covering 87.1\% of failures in our 302-case corpus.  Each pattern maps to
a taxonomy class (\textit{source\_bug}, \textit{lowering\_artifact},
\textit{verifier\_limit}, \textit{env\_mismatch}, \textit{verifier\_bug}).

The state trace parser (Stage 2) parses the remaining structure.  For each
BPF instruction, it extracts:
\begin{itemize}
  \item Instruction index, opcode, and mnemonic
  \item Pre/post-state per live register (type, \texttt{umin/umax},
        \texttt{smin/smax}, offset, packet range, provenance ID)
  \item BTF source annotation (file, line, column) if present
  \item Backtracking links from \texttt{mark\_precise} annotations
  \item Branch merge points with state at each join
\end{itemize}

The primary challenge is format variability.  Register state can appear before
or after the instruction, in branch merge lines, in backtracking annotations,
or across multiple lines.  The parser normalizes all variants into a uniform
\texttt{TracedInstruction} representation.

\textbf{Backtracking chain extraction.}  The verifier's own
\texttt{mark\_precise} backward pass is emitted in the log as
\texttt{regs=R stack=S before K: (op)~...} annotations.  \sys extracts
these into a \texttt{BacktrackChain} structure: a sequence of
(instruction\_index, registers\_tracked) pairs.  This is the verifier's own
root-cause chain, expressed as debug text; \sys is the first tool to
extract and structure it.

\subsection{Proof Obligation Inference}
\label{sec:obligation-inference}

The verifier trace contains thousands of abstract state transitions per
execution path; analyzing all of them would produce noise.  The proof
obligation serves as a \emph{focus mechanism}: given the error message and
the register state at the rejection point, \sys infers which safety
condition the verifier needed---the \emph{proof obligation}---expressed
as a formal predicate over register state.  This predicate then directs
the state-transition analysis in Section~3.4 to the relevant registers
and state dimensions.

\sys supports nineteen obligation families, shown in Table~\ref{tab:obligations}.
The error message identifies the obligation \emph{family}.  The register state
at the rejection point provides concrete parameters.  \sys instantiates the
predicate template with these parameters.

\begin{table}[t]
  \centering
  \footnotesize
  \caption{Proof obligation families supported by \sys (covering
    94.3\% of the 262-case evaluation corpus; representative families shown,
    nineteen supported in total).}
  \label{tab:obligations}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{llp{2.6cm}}
    \toprule
    \textbf{Family} & \textbf{Predicate} & \textbf{Example error} \\
    \midrule
    \texttt{packet\_access}     & \texttt{type==pkt \&\& off+sz<=r}      & invalid access to packet \\
    \texttt{map\_value\_bounds} & \texttt{0<=off \&\& off+sz<=val\_sz}   & invalid map value access \\
    \texttt{null\_check}        & \texttt{type!=*\_or\_null}              & map\_value\_or\_null deref \\
    \texttt{stack\_access}      & \texttt{fp\_off within frame bounds}   & invalid indirect read \\
    \texttt{helper\_arg\_type}  & \texttt{type==expected\_arg\_type}     & R1 scalar expected pkt \\
    \texttt{scalar\_bounds}     & \texttt{smin>=0 \&\& umax<=limit}      & unbounded min value \\
    \texttt{reference\_release} & \texttt{all refs released before exit} & Unreleased reference id=N \\
    \texttt{context\_access}    & \texttt{off+sz<=ctx\_size}             & invalid bpf\_context access \\
    \texttt{alignment}          & \texttt{off \% align == 0}             & misaligned access \\
    \texttt{type\_safety}       & \texttt{type matches expected}         & R1 inv expected fp \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

This predicate instantiation is not pattern matching on error text.  The same
error message (\texttt{invalid access to packet}) with different register
states at the rejection point produces different predicate instances with
different parameters.  The predicate is grounded in the verifier's type system:
for packet access, the verifier literally checks
\texttt{reg.off~+~access\_size~<=~reg.range}; \sys infers this from the
register fields at the rejection point.

\textbf{Inference algorithm.}  For each error ID, \sys defines:
(1) which register(s) contain the failing object (extracted from the rejection
line), (2) which predicate template applies (from the obligation family), and
(3) how to extract concrete parameters from the register state dump.  The
resulting predicate is a boolean function over register state that can be
evaluated at any point in the trace.

\subsection{Abstract State Transition Detection}

The core of \sys is detecting \emph{safety-relevant abstract state transitions}
across the verifier's execution trace.  Given the instantiated predicate $P$
from Section~\ref{sec:obligation-inference} as a focus mechanism, \sys
evaluates $P$ against the abstract state at every instruction, producing a
status sequence:
\[
  \underbrace{?, \ldots, ?}_{\text{unknown}},
  \underbrace{\top, \ldots, \top}_{\text{satisfied}},
  \underbrace{\bot, \ldots, \bot}_{\text{violated}}
\]

Each transition in this sequence corresponds to a concrete abstract state
change (e.g., a bounds collapse, type downgrade, or provenance loss) at a
specific instruction.  \sys labels each transition:
\begin{itemize}
  \item \emph{proof\_established}: the abstract state transition where $P$ becomes
        satisfied (\texttt{?} $\to$ \texttt{true})---e.g., a bounds check
        narrows a register's range
  \item \emph{proof\_holds}: instructions where the abstract state preserves $P$
  \item \emph{proof\_lost}: the abstract state transition where $P$ goes from
        satisfied to violated (\texttt{true} $\to$ \texttt{false})---the
        \emph{transition witness}, e.g., an OR instruction collapses bounds
  \item \emph{rejected}: the final error instruction (always identified)
\end{itemize}

If $P$ is never satisfied, the status is \textit{never\_established} (a source
bug: the required abstract state was never produced, indicating a missing safety
check).
If $P$ is satisfied but a subsequent state transition destroys it before the
rejection, the status is \textit{established\_then\_lost} (a lowering artifact:
the source has a valid check but compiler-generated instructions produce an
abstract state transition that the verifier's domain cannot track).

\textbf{Key distinction from heuristic approaches.}  The transition witness is
not ``detect a bounds collapse pattern.''  It is ``evaluate the specific
safety predicate at each abstract state and find the exact instruction whose
state transition broke it.''  Different predicates identify different
transition witnesses on the same trace.  This is formally grounded in the
verifier's abstract domain, not in ad hoc pattern detection.

\textbf{Register value lineage.}  Predicates reference registers, but register
names are reused across the trace.  A value computed in R0 may be copied to R3
before the access.  \sys tracks value identity across register moves and
copies.  If R3 is defined as a copy of R0 (\texttt{r3 = r0}), and the
obligation predicate references the packet range of R0, \sys continues
tracking the range on R3 for subsequent instructions.  This register value
lineage is essential for correctly identifying proof-established and proof-lost
events across LLVM's register allocation.

\textbf{Proof propagation analysis.}  For lowering artifact detection, \sys
additionally checks whether the proof established at the bounds-check site
\emph{propagates} to the register used at the access site.  If a different
register is used for the access than the one whose range was established at
the check (a common LLVM pattern), \sys classifies this as a lowering
artifact regardless of whether the proof predicate was technically satisfied
at some earlier instruction.

\subsection{Formal Foundation: Abstract State Transition Analysis}
\label{sec:formal-foundation}

The state transition detection described above can be understood as a
\emph{second-order abstract interpretation}: \sys applies abstract
interpretation to the \emph{output} of another abstract
interpreter~\cite{cousot1977}.  This section formalizes the framework,
which applies to any abstract interpreter that emits per-step states.

\subsubsection*{Two layers of abstract interpretation}

\textbf{Layer 1} is the eBPF verifier itself.  Its input is BPF
bytecode; its abstract domain $D_1$ consists of register types, scalar
bounds $[\texttt{umin},\texttt{umax}]$, pointer offsets, and packet ranges.
Its output is a trace $T = (s_0, s_1, \ldots, s_n)$ where each $s_i \in D_1$
is the abstract state after the $i$-th instruction.

\textbf{Layer 2} is \sys.  Its input is the trace $T$; it analyzes
abstract state transitions $(s_{i-1}, s_i)$ at each step, focused by a
safety predicate $P$, and outputs a sequence of proof lifecycle labels
that identify where and how the proof broke.

\begin{definition}[Proof status lattice]
\label{def:lattice}
The proof status lattice is
$\mathcal{L} = \{\bot, \mathit{unknown}, \mathit{satisfied}, \mathit{violated}\}$
with ordering
$\bot \sqsubseteq \mathit{unknown} \sqsubseteq \mathit{satisfied}$
and
$\bot \sqsubseteq \mathit{unknown} \sqsubseteq \mathit{violated}$,
where $\mathit{satisfied}$ and $\mathit{violated}$ are incomparable.
The bottom element~$\bot$ represents an uninitialized status
(relevant registers not yet present in the abstract state);
$\mathit{unknown}$ represents a state where the predicate is evaluable but the
relevant registers are not yet constrained.  Each transition between lattice
elements corresponds to a safety-relevant abstract state transition in the
verifier trace.
\end{definition}

\begin{definition}[State transition transfer function]
\label{def:transfer}
Let $P : D_1 \to \{\mathit{true}, \mathit{false}, \mathit{unknown}\}$ be the
safety predicate instantiated from the rejection point
(\S\ref{sec:obligation-inference}).
For each traced instruction~$i$ with verifier state $s_i \in D_1$,
the transfer function $\tau_i : \mathcal{L} \to \mathcal{L}$ maps the
previous proof status to the status after observing the abstract state
transition at instruction~$i$:
\[
\tau_i(\ell) = \begin{cases}
  \mathit{sat} & P(s_i) \land \ell \in \{\mathit{unk}, \mathit{sat}\} \\[2pt]
  \mathit{vio} & \neg P(s_i) \land \ell = \mathit{sat} \\[2pt]
  \ell         & \text{otherwise}
\end{cases}
\]
\end{definition}

\noindent
The status sequence is computed by forward iteration:
$\ell_0 = \mathit{unknown}$,\;
$\ell_i = \tau_i(\ell_{i-1})$.

\begin{definition}[Transition witness]
\label{def:witness}
The transition witness is the smallest index $w$ such that
$\ell_{w-1} = \mathit{satisfied}$ and $\tau_w(\ell_{w-1}) = \mathit{violated}$.
This is the exact instruction where the proof breaks.
If no such $w$ exists and $\ell_n = \mathit{violated}$, the proof was
\emph{never established}.
\end{definition}

\begin{proposition}[Soundness of lifecycle labels]
\label{prop:soundness}
If \sys labels instruction~$i$ with
$\ell_i = \mathit{satisfied}$, then for all concrete states
$c \in \gamma(s_i)$ (where $\gamma$ is the concretization function of the
verifier's abstract domain), the safety property encoded by~$P$ holds.
\end{proposition}
\begin{proof}[Proof sketch]
The verifier is a sound abstract interpreter: $s_i$ over-approximates all
concrete states reachable at instruction~$i$~\cite{gershuni2019simple}.
The obligation predicate $P$ is monotone with respect to the verifier's
partial order on~$D_1$ (tighter bounds imply satisfaction if looser bounds
already satisfy).  Therefore $P(s_i) = \mathit{true}$ implies
$P(c) = \mathit{true}$ for all $c \in \gamma(s_i)$.
\end{proof}

\textbf{Backward obligation slice.}
Given the transition witness $w$, the \emph{backward obligation slice} is
\[
  S = \{ i < w \mid \exists\, r \in \mathit{regs}(P) .\;
    \text{instruction } i \text{ writes to } r \}
\]
i.e., all instructions before $w$ that write to registers appearing in the
obligation predicate~$P$.  When \texttt{mark\_precise} backtracking
information is available in the trace, $S$ is refined to include only
instructions on the backtracking chain, yielding a tighter slice.

\textbf{Generalization beyond eBPF.}
Abstract state transition analysis applies to any abstract interpreter that
outputs per-step abstract states.  The requirements are:
(1)~per-step abstract states are emitted,
(2)~safety properties are expressible as predicates over the abstract domain,
and (3)~the trace is ordered.
The key insight is domain-independent: given a sequence of abstract states
$[s_0, \ldots, s_n]$ and a safety predicate~$P$, detecting the transition
$(s_{w-1}, s_w)$ where $P$ changes from satisfied to violated locates the
proof-loss point regardless of what the abstract domain represents.
Rust's borrow checker (lifetime predicates over borrow state), WebAssembly
validators (type predicates over operand stack state), and Java bytecode
verifiers (type predicates over stack frame state) all satisfy these
requirements---suggesting that abstract state transition analysis is a
general technique for improving diagnostic quality in verified language
runtimes.

\subsection{BTF Source Correlation}

\sys maps each detected state transition event (proof established, proof lost,
rejected) to its source location via BTF \texttt{line\_info}
annotations~\cite{linuxbtf}.
When the verifier emits a source-location comment before an instruction (e.g.,
\texttt{; foo.c:42}), \sys records the mapping.  Multiple consecutive bytecode
instructions from the same source line are merged into a single span.

The result is 3--5 source-level spans, each labeled with a proof lifecycle
role and annotated with the register state change at that point.  When BTF
annotations are absent (34.4\% of our corpus, primarily Stack Overflow cases
where log fragments lack BTF context), \sys falls back to bytecode-level
spans (instruction indices only).

BTF coverage is a data quality issue, not a parser limitation: kernel
selftest cases have 98.7\% BTF coverage, confirming that the correlation works
correctly when the input has BTF annotations.

\subsection{Diagnostic Rendering}

\sys produces two output formats from the same state transition analysis:

\textbf{Human-readable Rust-style output.}  Modeled on Rust compiler
diagnostics~\cite{rustdiag2016}, the output shows multiple source spans
with causal labels, register state changes at each transition, and
\texttt{note}/\texttt{help} annotations.  The format is designed to be
readable in a terminal, an IDE, or a CI log without any tool support.

\textbf{Structured JSON.}  A machine-readable format containing
\texttt{error\_id}, \texttt{taxonomy\_class}, \texttt{proof\_status}, an array
of \texttt{spans} (each with role, source location, instruction index, and
state change), the instantiated obligation predicate, and \texttt{note}/\texttt{help}
text.  This format is designed for consumption by LLM agents (replacing raw
log text in prompts), CI systems (structured failure annotations), and IDE
plugins.

\subsection{Implementation Notes}

\sys is implemented in Python ($\sim$14,613 lines across five modules:
\texttt{log\_parser}, \texttt{trace\_parser}, \texttt{proof\_engine},
\texttt{source\_correlator}, and \texttt{rust\_diagnostic}), with 268 unit
tests covering obligation inference, predicate evaluation, backward slicing,
and transition witness detection on hand-crafted and real-corpus traces.
It defines 23 error IDs (\sys{}-E001 through E023) and nineteen obligation
families.

\textbf{Source-code independence.}  \sys requires only the verifier log
text as input---no object files, source files, or external debug information.
When BTF \texttt{line\_info} annotations are present in the log, \sys maps
proof events to source-level spans; when BTF is absent, it falls back to
bytecode-indexed spans.  For already-loaded programs, \texttt{bpftool prog
dump xlated linum} can supply supplementary source context, but this is
optional.

\textbf{Language independence.}  Because \sys analyzes the verifier trace
at the BPF bytecode level, it is agnostic to the source language.
Table~\ref{tab:per-language} breaks down diagnostic performance by source
language across all 302 cases (including ineligible ones).
Diagnostic success is uniformly high: 85.8\% for C, 95.2\% for Rust (Aya),
and 100\% for Go (Cilium).  The lower obligation inference rate for Rust
(40.0\% vs.\ 93.2\% for C) and the near-zero BTF coverage for non-C cases
reflect the log richness available in the corpus (Rust and Go cases are
primarily from GitHub issues with truncated logs), not a language-specific
limitation in the parser.

\begin{table}[t]
\centering
\scriptsize
\caption{Per-language \sys diagnostic performance (302 cases).}
\label{tab:per-language}
\begin{tabular}{lrrrr}
\toprule
\textbf{Lang.} & \textbf{Cases} & \textbf{Diag Success} & \textbf{Obligation} & \textbf{BTF} \\
\midrule
C    & 274 & 235 (85.8\%) & 219/235 (93.2\%) & 170 (62.0\%) \\
Rust &  21 &  20 (95.2\%) &   8/20  (40.0\%) &   1 (4.8\%)  \\
Go   &   7 &   7 (100\%)  &   5/7   (71.4\%) &   1 (14.3\%) \\
\bottomrule
\end{tabular}
\end{table}

%% ==============================
\section{Evaluation}
%% ==============================

We evaluate \sys against six questions:
\begin{itemize}
  \item[\textbf{Q1}] Does \sys generate diagnostics reliably at scale?
  \item[\textbf{Q2}] What fraction of cases get full proof obligation coverage?
  \item[\textbf{Q3}] Do {\sys}'s source spans cover actual fix locations?
  \item[\textbf{Q4}] Do \sys diagnostics improve LLM-assisted repair?
  \item[\textbf{Q5}] How does \sys compare to Pretty Verifier?
  \item[\textbf{Q6}] What is the runtime overhead?
\end{itemize}

\subsection{Corpus and Methodology}
\label{sec:corpus}

Table~\ref{tab:corpus} describes our evaluation corpus.  The primary corpus
comprises 302 real verifier failure cases from three sources: 200 kernel
selftests (with \texttt{\_\_msg()} annotations specifying expected verifier
errors), 76 Stack Overflow questions with attached verifier logs, and 26
GitHub issues from Cilium, Aya, and Katran.  Of the 302 cases, 262 have
verifier logs of sufficient length for diagnostic evaluation ($\geq$50
characters); these form our evaluation corpus.

\begin{table}[t]
  \centering
  \small
  \caption{Evaluation corpus.}
  \label{tab:corpus}
  \begin{tabular}{lrrrr}
    \toprule
    \textbf{Source} & \textbf{Cases} & \textbf{Eligible} & \textbf{BTF} & \textbf{Known fix} \\
    \midrule
    Kernel selftests & 200 & 171 & 98.7\% & 200 \\
    Stack Overflow   & 76  & 65  & 1.5\%  & 66  \\
    GitHub issues    & 26  & 26  & 7.7\%  & 15  \\
    \midrule
    \textbf{Total}   & \textbf{302} & \textbf{262} & \textbf{65.6\%} & \textbf{281} \\
    \bottomrule
  \end{tabular}
\end{table}

Thirty cases are manually labeled with ground-truth taxonomy by a domain expert
(the first author), achieving Cohen's $\kappa = 0.652$ against the heuristic
classifier.  The heuristic classifier agrees with manual labels in 76.7\% of
cases overall, but only 33.3\% on lowering artifacts---confirming that this is
the hardest class to diagnose from error messages alone.

The taxonomy distribution across the 262-case evaluation corpus:
source\_bug 48.5\%, env\_mismatch 31.3\%, lowering\_artifact 12.6\%,
verifier\_limit 7.6\%.

\subsection{Batch Reliability and Obligation Coverage (Q1, Q2)}
\label{sec:batch}

We ran \sys on all 262 eligible cases.  Table~\ref{tab:batch} reports the
results.

\begin{table}[t]
  \centering
  \small
  \caption{Batch diagnostic evaluation on 262 cases (Q1, Q2).}
  \label{tab:batch}
  \begin{tabular}{lr}
    \toprule
    \textbf{Metric} & \textbf{Result} \\
    \midrule
    Diagnostic generation success   & 262/262 (100\%) \\
    Proof obligation inferred       & 247/262 (94.3\%) \\
    BTF source correlation          & 172/262 (65.6\%) \\
    \midrule
    Proof-established span          & 115/262 (43.9\%) \\
    Proof-lost span                 & 99/262 (37.8\%) \\
    Causal chain extracted          & 24/262 (9.2\%) \\
    Proof status: never\_established     & 129/262 (49.2\%) \\
    Proof status: established\_then\_lost & 99/262 (37.8\%) \\
    \bottomrule
  \end{tabular}
\end{table}

\sys generates a structured diagnostic for every case with zero crashes.
Proof obligation coverage of 94.3\% (247/262) means that for nineteen in twenty
cases, \sys can state the exact predicate the verifier needed and evaluate
it at every instruction.  The remaining 6\% involve environment errors
(Permission denied, build failures) rather than true verifier rejections, and
fall outside the nineteen currently supported obligation families.  We
explicitly characterize this scope limitation in Section~\ref{sec:discussion}.

The proof status distribution reflects the failure mix: 49.2\% are
\textit{never\_established} (source bugs with no proof at any point), 37.8\%
are \textit{established\_then\_lost} (proofs that exist in source but are
destroyed during lowering or across program structure).  This 37.8\% is the
population where \sys provides its strongest differentiating value.
Of these, 24 cases (9.2\%) have structured causal chains extracted via
\texttt{mark\_precise} backward slicing (Section~\ref{sec:formal-foundation}),
connecting the proof-loss instruction to the final rejection through
register-level dependency edges.

\textbf{Span coverage (Q3).}  For cases with known fixes, 12/14 manually
annotated cases (85.7\%) have at least one \sys span overlapping the fix
location; on kernel selftests, 85/102 (83.3\%) of rejected spans match the
expected error instruction.  The overall 38.4\% (101/263) figure is deflated
by Stack Overflow cases where fix locations are described in prose rather than
as line numbers---a corpus limitation, not a parser one.

\subsection{LLM Repair Experiment (Q4)}
\label{sec:repair}

We evaluate whether \sys diagnostics help an LLM generate better repairs.
We use an A/B design: the same LLM (GPT-4.1-mini) receives either (A) buggy
code plus raw verifier log, or (B) buggy code plus raw log plus {\sys}'s
Rust-style diagnostic.  We measure fix-type accuracy (does the LLM choose the
correct type of fix?), root-cause targeting (does it target the right location?),
and semantic similarity to the known correct fix.

Table~\ref{tab:repair} shows results on 54 cases (10 lowering artifacts,
28 source bugs, 8 verifier limits, 8 env mismatches).

\begin{table}[t]
  \centering
  \footnotesize
  \caption{A/B LLM repair experiment (54 cases).  Condition~A: raw verifier
    log only.  Condition~B: raw log + \sys diagnostic.}
  \label{tab:repair}
  \resizebox{\columnwidth}{!}{\begin{tabular}{lrrr}
    \toprule
    \textbf{Metric} & \textbf{A (raw log)} & \textbf{B (+\sys)} & \textbf{$\Delta$} \\
    \midrule
    Overall location accuracy   & 53/54 (98.1\%) & 48/54 (88.9\%) & $-$9pp \\
    Overall fix-type accuracy   & 46/54 (85.2\%) & 43/54 (79.6\%) & $-$6pp \\
    \textbf{Lowering fix type}  & \textbf{3/10 (30\%)} & \textbf{6/10 (60\%)} & \textbf{+30pp} \\
    Source bug fix type         & 27/28 (96.4\%) & 23/28 (82.1\%) & $-$14pp \\
    Verifier limit fix type     & 8/8 (100\%)  & 7/8 (87.5\%)  & $-$12.5pp \\
    Env mismatch fix type       & 8/8 (100\%)  & 7/8 (87.5\%)  & $-$12.5pp \\
    \bottomrule
  \end{tabular}}
\end{table}

The headline overall fix-type accuracy shows Condition A marginally ahead
(85.2\% vs 79.6\%), but the per-class breakdown tells the story.  On lowering
artifacts---the class where raw error messages are most misleading---\sys
diagnostics double the fix-type accuracy: 3/10 (30\%) with raw logs versus
6/10 (60\%) with \sys diagnostics, a +30\,pp gain.  In Condition A, the LLM
sees an error like ``unbounded min value'' and adds another bounds check (wrong).
In Condition B, it sees that the bounds check at line 3 \emph{established} the
proof, the \texttt{htons} call at line 7 \emph{destroyed} it, and it correctly
applies a scalar clamp.

The overall regression on non-lowering classes (Condition B slightly below A)
has a known root cause: several source-bug cases received \sys output pointing
to a BTF metadata issue rather than the actual logic fix (e.g., BTF/func\_info
regeneration advice on dynptr and iterator cases), pushing the LLM away from
the correct repair.  The raw log for these cases already named the specific
contract violation, and the generic \sys output added noise.  This is a
known issue with BTF-absent traces and is targeted for improvement.

We present this as evidence that {\sys}'s value is concentrated on the
lowering-artifact class, where proof-trace analysis provides qualitatively
different information not available in raw logs.

\subsection{Comparison with Pretty Verifier (Q5)}
\label{sec:pvcomparison}

We compared \sys against Pretty Verifier on the 30 manually labeled cases.
Table~\ref{tab:pvcomp} summarizes the results.

\begin{table}[t]
  \centering
  \footnotesize
  \caption{\sys vs.\ Pretty Verifier on 30 manually labeled cases (top)
    and the full 262-case corpus (bottom).}
  \label{tab:pvcomp}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lrr}
    \toprule
    \textbf{Metric} & \textbf{Pretty Verifier} & \textbf{\sys} \\
    \midrule
    \multicolumn{3}{l}{\textit{30-case manually labeled subset}} \\
    Overall classification accuracy  & 19/30 (63\%) & 25/30 (83\%) \\
    Lowering artifact accuracy       & 1/6 (17\%)   & 4/6 (67\%)  \\
    Root-cause localization          & 0/30 (0\%)   & 12/30 (40\%) \\
    Cases with actionable diagnosis  & 5/30 (17\%)  & 20/30 (67\%) \\
    Crash-free operation             & 22/30 (73\%) & 30/30 (100\%) \\
    \midrule
    \multicolumn{3}{l}{\textit{Full 262-case corpus}} \\
    Crash-free operation             & 234/262 (89.3\%) & 262/262 (100\%) \\
    Produces recognized output       & 75/262 (28.6\%)  & 262/262 (100\%) \\
    Root-cause localization          & 0/262 (0\%)      & 53/262 (20.2\%) \\
    Multi-span diagnostic            & 0/262 (0\%)      & 115/262 (43.9\%) \\
    Causal chain                     & 0/262 (0\%)      & 24/262 (9.2\%) \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

The key distinction is not classification accuracy.  It is root-cause
localization.  Pretty Verifier finds root cause in 0/30 cases because it
does not analyze state evolution.  \sys finds an earlier proof-loss site
in 12/30 cases (40\%)---and in 4/4 of these cases, the proof-loss site is a
\emph{different instruction} than the final rejection, providing qualitatively
different guidance.

\textbf{Expanded 262-case comparison.}  The 30-case results generalize to the
full corpus (Table~\ref{tab:pvcomp}, bottom).  Pretty Verifier crashes on
28/262 cases (10.7\%) and produces recognized output on only 75/262 (28.6\%);
the remaining 60.3\% receive ``Error not managed.''  \sys processes all 262
cases with zero crashes, produces multi-span diagnostics on 115 (43.9\%),
and localizes an earlier root-cause instruction on 53 (20.2\%).  The
separation is sharpest on lowering artifacts: Pretty Verifier handles 5/33
and crashes on 8/33, while \sys produces multi-span output on 24/33.

Source localization also differs fundamentally.  Pretty Verifier maps source
via \texttt{llvm\allowbreak-objdump} on the compiled object file (unavailable
in most deployment contexts).  \sys uses BTF annotations embedded in the log
itself, achieving 65.6\% coverage without any external files.

\subsection{Runtime Overhead (Q6)}
\label{sec:latency}

\sys processes all 262 cases with median latency 25.3\,ms (P95: 41.2\,ms,
max: 89.3\,ms, scaling linearly with log length at Pearson $r = 0.802$).
All cases complete in under 100\,ms---comfortably within interactive bounds
and negligible compared to a single LLM API call (1--10\,s).


%% ==============================
\section{Discussion and Limitations}
\label{sec:discussion}
%% ==============================

\subsection{Scope and Honest Limitations}

\textbf{94\% obligation coverage.}  Nineteen obligation families cover 94.3\% of
cases.  The remaining 6\% involve environment errors (Permission denied, build
failures) rather than true verifier rejections; these fall outside the scope of
proof-trace analysis.  The predicate framework is extensible, and adding a new
family requires defining the predicate template and the parameter extraction
rules.  We provide an explicit enumeration of the nineteen supported families
(Table~\ref{tab:obligations}) so readers can assess scope.

\textbf{BTF coverage.}  34.4\% of cases lack BTF annotations (primarily Stack
Overflow fragments).  Without BTF, \sys produces bytecode-level spans
(instruction indices) rather than source-level spans.  This degrades human
readability but not the underlying predicate analysis.  The 98.7\% BTF coverage
on kernel selftests confirms that the correlation is correct when inputs are
well-formed.

\textbf{Path-insensitive slicing.}  {\sys}'s backward slice from the
transition witness is bounded and path-insensitive.  It will not correctly
handle all loop- or alias-sensitive proof loss patterns.  We scope the slice
as an explanatory aid after the main predicate/transition detection, and
validate it empirically rather than claiming formal precision.

\textbf{LLM repair experiment uses proxy metrics.}  The A/B experiment uses 54
cases and proxy metrics (fix-type classification) rather than verifier-pass
outcomes.  The regression on source-bug cases caused by BTF-absent traces
pointing toward metadata issues is a known failure mode.  A full re-run with
updated prompts and a verifier-pass oracle is planned.

\textbf{No cross-kernel stability evaluation.}  The verifier's log format
varies across kernel versions.  We have not yet evaluated \sys across
multiple kernel versions.  Prior work~\cite{depsurf2025} finds that 83\% of
eBPF extensions are affected by at least one kernel mismatch; this is an
important axis for future work.

\subsection{Upstream Potential}

{\sys}'s output could become part of the kernel's own diagnostic
infrastructure.  The structured JSON format and 23 error IDs are designed
to be stable and extensible.  The proof obligation catalog could inform
improvements to verifier error messages.  The Rust-style rendering could
be integrated into \texttt{bpftool} or the \texttt{libbpf} loader, so
developers receive structured diagnostics directly from the load path.

%% ==============================
\section{Related Work}
%% ==============================

\subsection{eBPF Verifier Complexity and Developer Pain}

Jia et al.~\cite{hotos2023verif} argue that kernel-extension verification
is ``untenable'' as the extension surface grows; \sys addresses the near-term
reality that millions of C/Rust eBPF programs run against the current verifier.
Rex~\cite{rex2025} studies 72 verifier workaround commits, confirming 44.4\% are
LLVM code-generation changes; Rex explains \emph{why} such failures exist, \sys
explains \emph{this specific failure instance} at load time.  Deokar et
al.~\cite{deokar2024} find 19.3\% of 743 Stack Overflow questions are
verifier-related, quantifying the pain point \sys addresses.

\subsection{Diagnostic Tools}

Pretty Verifier~\cite{prettyverifier2025} applies 91 regex patterns to the final
verifier error line, producing a single-span explanation; it cannot detect
proof-loss transitions and crashes on 10.7\% of our corpus.  \sys analyzes
abstract state transitions across the complete execution trace---a different
level of analysis that enables root-cause localization and lowering artifact
diagnosis.
The \texttt{ebpf-verifier-errors} repository~\cite{ebpfverifdict} crowdsources
(log, fix) pairs as data, but provides no automated analysis.

\subsection{LLM-Based eBPF Tools}

Kgent~\cite{kgent2024} feeds raw verifier output verbatim to an LLM repair loop;
{\sys}'s structured diagnostics could serve as Kgent's preprocessor, replacing
unstructured register dumps with labeled causal spans.  SimpleBPF~\cite{simplebpf2025}
generates a high-level DSL and explicitly notes that raw-log retry ``was not effective'';
\sys addresses the general case (arbitrary handwritten C/Rust) that DSLs cannot
replace.  K2~\cite{k22023} optimizes eBPF programs for performance, a goal
orthogonal to failure diagnosis.

\subsection{Static Analysis and Diagnostics}

{\sys}'s approach is inspired by counterexample analysis in model checking:
reconstruct why verification failed from the evidence trace.  Abstract
interpretation~\cite{cousot1977} and its formalization for eBPF~\cite{gershuni2019simple}
ground {\sys}'s state transition analysis.  Program slicing~\cite{weiser1981} motivates
backward dependency extraction from the transition witness.  Rust's compiler
diagnostics~\cite{rustdiag2016} pioneered multi-span source-level errors with
causal labels; research on compiler error messages~\cite{errormessages2014} confirms
that pointing at the wrong location significantly harms developer productivity.

%% ==============================
\section{Conclusion}
%% ==============================

The eBPF verifier already emits everything needed to understand why a program
is rejected---but that information is buried in verbose, thousand-line traces.
\sys demonstrates that a simple yet powerful idea, analyzing abstract state
transitions in the verifier's execution trace, can transform these opaque
logs into precise, actionable diagnostics. The clearest payoff is for
compilation-induced failures, where existing tools localize root causes in 0\%
of cases; \sys pinpoints the proof-loss point in 67\% and boosts automated
repair accuracy by 30 percentage points. At 25.3\,ms median latency, entirely
in userspace, and with no kernel modifications, \sys is practical for
integration into existing eBPF development workflows. As eBPF programs grow in
complexity and the verifier continues to evolve, abstract state transition
analysis offers a principled, generalizable path to making verification
failures comprehensible.

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
